### 2022-03-02 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@5ab839c230e8422cceddc0ce741a933b95bbf9fd 🚀

The dataset used for numerical experiments is composed of 64000 such
\((\xi, \nu)\) pairs, on which four machines are trained: a decision
tree regressor, a boosted regression tree, a ridge regressor, and a
random forest regressor. All models were taken from the \texttt{MLJ.jl}
package (Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7
(Bezanson et al., 2017). All machines use the default parameterization;
this is an obvious deviation from best practices, as the hyperparameters
of any machine require training before its application on a real
dataset. As we use 64000 such datasets, this would require 256000 unique
instances of tweaking the hyperparameters, which is not realistic.
Therefore, we assume that the default parameterizations are comparable
across networks. All machines return a quantitative prediction, usually
(but not necessarily) in \([0,1]\), which is proportional (but not
necessarily linearly) to the probability of an interaction between \(i\)
and \(j\). Nevertheless, the ROC-AUC and PR-AUC (and therefore the
thresholds) can be measured by integrating over the domain of the values
return by each machine.

@@

After the simulations were completed, we removed all runs (\emph{i.e.}
pairs of \(\xi\) and \(\nu\)) for which at least one of the following
conditions was met: the accuracy was 0, the true positive or true
negative rates were 0, the connectance was larger than 0.25. This
removes both the obviously failed model runs, and the networks that are
more densely connected compared to the connectance of empirical food
webs (and are therefore less difficult to predict, being less
imbalanced; preliminary analyses of data with a connectance larger than
0.3 revealed that all machines reached consistently high performance).

@@

The previous results revealed that the measure of classification
performance responds both to the bias in the training set \emph{and} to
the connectance of the network; from a practical point of view,
assembling a training set requires to withold positive information,
which in ecological networks are very scarce (and typically more
valuable than negatives, on which there is a doubt). For this reason,
across all values of connectance, we measured the training set balance
that maximized a series of performance measures. When this value is
high, the training set needs to skew more positive in order to get a
performant model; when this value is about 0.5, the training set needs
to be artificially balanced to optimize the model performance. These
results are presented in fig.~\ref{fig:optimbias}.

@@

(\textbf{Xie2017ComCom?}) - most networks have SBM structure ---
(\textbf{Valdovinos2019MutNet?}) matching + forbidden
(\textbf{Olesen2011MisFor?}), coming up with matching rules that
allow/forbid links can make predictions easier
(\textbf{Strona2017ForPer?}); but valid for most type of interactions as
long as we can match yes/no to numeric predictors

@@

>>>>

The dataset used for numerical experiments is composed of a grid of 35
values of connectance (from 0.011 to 0.5) and 35 values of \(\nu\) (from
0.02 to 0.98); for each pair of values, 500 networks are generated and
predicted. For each network, we train four machines: a trait-based k-NN
(\emph{e.g.} \textbf{Desjardins-Proulx2017EcoInt?}), a regression tree,
a regression random forest, and a boosted regression tree. Following
results from Pichler et al. (2020), linear models have not been
considered (in any way, the relationship in the simulated networks is
non-linear). The point of these numerical experiments is \emph{not} to
recommend the best model (this is likely problem-specific), but to
highlight a series of recommendations that would work for supervised
learning tasks. All models were taken from the \texttt{MLJ.jl} package
(Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7 (Bezanson et
al., 2017). All machines use the default parameterization; this is an
obvious deviation from best practices, as the hyperparameters of any
machine require training before its application on a real dataset. As we
use 612500 such datasets, this would require over 2 millions unique
instances of tweaking the hyperparameters, which is prohibitive from a
computing time point of view. An important thing to keep in mind is that
the problem we simulate has been designed to be simple to solve: we
expect all machines with sensible default parameters to fare well ---
the results presented in the later sections show that this assumption is
warranted, and we further checked that the models do not overfit by
ensuring that there is never more than 5\% of difference between the
accuracy on the training and testing sets. All machines return a
quantitative prediction, usually (but not necessarily) in \([0,1]\),
which is proportional (but not necessarily linearly) to the probability
of an interaction between \(i\) and \(j\). The ROC-AUC and PR-AUC (and
therefore the thresholds) can be measured by integrating over the domain
of the values return by each machine, but in order to make the
average-based ensemble model more meaningful, all predictions are
expressed in \([0,1]\).

@@

After the simulations were completed, we removed all runs (\emph{i.e.}
triples of model, \(\xi\), and \(\nu\)) for which at least one of the
following conditions was met: the accuracy was 0, the true positive or
true negative rates were 0, the connectance was larger than 0.25. This
removes both the obviously failed model runs, and the networks that are
more densely connected compared to the connectance of empirical food
webs (and are therefore less difficult to predict, being less
imbalanced; preliminary analyses of data with a connectance larger than
0.3 revealed that all machines reached consistently high performance).

@@

The previous results revealed that the measure of classification
performance responds both to the bias in the training set \emph{and} to
the connectance of the network; from a practical point of view,
assembling a training set requires one to withhold positive information,
which in ecological networks are very scarce (and typically more
valuable than negatives, on which there is a doubt). For this reason,
across all values of connectance, we measured the training set balance
that maximized a series of performance measures. When this value is
high, the training set needs to skew more positive in order to get a
performant model; when this value is about 0.5, the training set needs
to be artificially balanced to optimize the model performance. These
results are presented in fig.~\ref{fig:optimbias}.

@@

@@

One key element for real-life data that can make the prediction exercise
more tractable is that some interactions can safely be assumed to be
impossible; indeed, a lot of networks admit a stochastic block model as
a good approximation (\emph{e.g.} \textbf{Xie2017ComCom?}). In
ecological networks, this can be due to spatial constrains
(\textbf{Valdovinos2019MutNet?}), or to the long-standing knowledge that
some links are ``forbidden'' due to traits (\textbf{Olesen2011MisFor?})
or abundances (\textbf{Canard2014EmpEva?}). The matching rules
(\textbf{Strona2017ForPer?}) can be incorporated in the model either by
adding compatibility traits, or by \emph{only} training the model on
pairs of species that are not likely to be forbidden links. Besides
forbidden links, a real-life case that may arise is multi-interaction or
multi-layer networks (\textbf{Pilosof2017MulNat?}). These can be studied
using the same general approach outlined here, either by assuming that
pairs of species can interact in more than one way (wherein one would
train a model for each type of interaction, based on the relevant
predictors), or by assuming that pairs of species can only have one type
of interaction (wherein this becomes a multi-label classification
problem).
